Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-26 robdml.tex
tex

However, while the destination hardness is boosted in the late phase of
training, the adversarial examples may still hamper the learning of a good
embedding space in the early phase.
%
At this point, we argue that learning from a strong adversary in the early
training phase (\ie, when the embedding space is not ``in-good-shape'') hampers the
generalization on benign examples.

@@

In other words, the desired destination hardness should be (1) relatively weak
in the early training phase, and (2) relatively strong in the late training
phase.
%
We name the family of pseudo-hardness functions that fulfills the two
conditions as ``Graduate Adversary''.
%
Additionally, if we have a strong prior knowledge on ``how hard the destination
hardness should be'', the pseudo-hardness function can be independent from
any benign triplet.

@@

For instance, if we assume that the destination hardness should remain
in the hardness range of Semihard~\cite{facenet}, the following function
satisfies the two condictions of Gradual Adversary, dubbed
``Simple Gradual Adversary'' (SGA):
%
\begin{equation}
	%
	g_\mathsf{SGA}(\bar{\ell}_{t-1}) =
	-\gamma \cdot \bar{\ell}_{t-1} ~ \in [-\gamma,0].
	%
\end{equation}
%
And the adversarial examples from $\text{HM}(H_\mathsf{S},g_\mathsf{SGA})$
can be used for adversarial training.
%
The design of this function will be empirically supported in the experiments
section.
%
The exploration of other possible pseudo-hardness functions is omitted 
for simplicity.

>>>>

Apart from the deficiency in the late phase of training, we speculate that
relatively strong adversarial examples may hinder the model from 
learning good embedding space for the benign examples in the very early phase
of training, hence influence the model performance on benign examples.

@@

Thus, a desired $H_\mathsf{D}$ should be (1) close to $H_\mathsf{S}$ in the
early training phase (indicated by a large loss value), and (2) clearly higher
than $H_\mathsf{S}$ in the late training phase (indicated by a small loss
value).
%
We name the two conditions as ``Graduate Adversary'' for 
pseudo-hardness functions.

Additionally, if we have a strong prior knowledge on ``how hard the destination
hardness should be'', the pseudo-hardness function can be independent from any
benign triplet.

@@

For instance, if we assume that the destination hardness should remain
in the hardness range of Semihard~\cite{facenet}, the following function
satisfies the two condictions of Gradual Adversary, dubbed
``Simple Gradual Adversary'' (SGA):
%
\begin{equation}
	%
	g_\mathsf{SGA}(\bar{\ell}_{t-1}) =
	-\gamma \cdot \bar{\ell}_{t-1} ~ \in [-\gamma,0].
	%
\end{equation}
%
And the adversarial examples from $\text{HM}(H_\mathsf{S},g_\mathsf{SGA})$
can be used for adversarial training.
%
The design of this function will be empirically supported in the experiments
section.
%
\cref{fig:ga}
%
The exploration of other possible pseudo-hardness functions is omitted 
for simplicity.
